Quantitative Auditing of Fairness Measures with Differentially Private Synthetic Data

### 2024-12-05 paper/paper.tex
sophisticated

Let $\set{X_i}$ be a set of discrete random variables indexed by a graph $G = (V,E)$, where $V$ represents the random variables $X_i$s and $E$ represents dependencies between these random variables. A \emph{Markov random field} is a probability distribution over $X_i$s, such that each random variable $X_i$, given its neighborhood in $G$, is conditionally independent of all other variables. Since edges represent dependencies, cliques in a Markov random field represent groups of variables that are all mutually dependent. As a machine learning model, there has been much development in the fitting and inference of Markov random fields\cite{koller2009probabilistic,murphy2023probabilistic}.

@@

As for privacy, on the other hand, it introduces risks of information leakage. Releasings of analyses on real data may inadvertently reveal sensitive information by data inference attacks. Attackers can exploit patterns in data outputs or combine outputs with external data to infer sensitive information.

Thus, we introduce a new framework where the auditor generates synthetic data based on real data upon retrieval of the real data, and then holds onto the synthetic data and discards the real data, preventing all further data breaches. The third-party retains the ability to audit all incoming future models as needed.

@@

We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by \cite{McKenna_Private-PGM_2021,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.

@@

Underneath the hood, the tool employs a Markov random field. The select step corresponds to marking cliques in a Markov random field, and the generate step corresponds to sampling by inference from the fitted Markov random field.

@@

In a perfect world where all correlation information is to be preserved, we may wish to make a completely connected graph. However, this was found to be intractable as the complexity of the problem would skyrocket.

To circumvent the complexity explosion, instead, \cite{mckenna2021winning} devised a technique where the mutual information of all the database attribute pairs is calculated, and then a maximum spanning tree is obtained with edge weights being the mutual information to form a skeleton tree-shaped Markov random field.

>>>>

Let $\set{X_i}$ be a set of discrete random variables indexed by a graph $G = (V,E)$, where $V$ represents the random variables $X_i$s and $E$ represents dependencies between these random variables. A \emph{Markov random field} is a probability distribution over $X_i$s, such that each random variable $X_i$, given its neighborhood in $G$, is conditionally independent of all other variables. Since edges represent dependencies, cliques in a Markov random field represent groups of variables that are all mutually dependent. As a machine learning model, there has been much development in the estimation and inference of Markov random fields\cite{koller2009probabilistic,murphy2023probabilistic}.

@@

As for privacy, on the other hand, it introduces risks of information leakage. Releasings of analyses on real data may inadvertently reveal sensitive information by data inference attacks. Attackers can exploit data patterns in outputs or combine outputs with external data to infer sensitive information.

Thus, we introduce a new framework where the auditor generates synthetic data based on real data upon retrieval of the real data, and then holds onto the synthetic data and discards the real data, preventing all further security and privacy violations. The third-party still retains the ability to audit all incoming future models as needed.

@@

We employed the tools of the winner of the 2018 NIST Differential Privacy Synthetic Data Challenge competition\cite{NIST2018} by \cite{nist_ryan_2018,McKenna_Private-PGM_2021,mckenna2021winning,mckenna2019graphical} and the fairness checker tool from our previous research\cite{yuan2024ensuring}.

@@

Underneath the hood, the tool employs a Markov random field. The select step corresponds to marking cliques in a Markov random field, and the generate step corresponds to sampling from the fitted Markov random field.

@@

In a perfect world where all correlation information is to be preserved, we may wish to make a completely connected graph. However, this is intractable as the complexity of the problem would skyrocket. Furthermore, algorithms for Markov random field favor graphs with specific shapes, such as trees.

To circumvent this complexity explosion, instead, \cite{mckenna2021winning} devised a technique where the mutual information of all the database attribute pairs is calculated, and then a maximum spanning tree is identified with edge weights being the mutual information to obtain a skeleton tree-shaped Markov random field.
